Timeliness of security updates for Android

### 2014-11-14 securityupdates.tex
Add some futher discussion of the proportioninsecure graph at the beginning of the experiments section

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
%This graph is explained further in XXX.
}
\label{fig:proportioninsecure}
\end{figure}

@@

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
This graph is explained further in \S\ref{sec:exp:versionsecurity}.
}
\label{fig:proportioninsecure}
\end{figure}

@@

\subsection{Experiment 0: vulnerability of Android devices}\label{sec:exp:versionsecurity}
In Figure~\ref{fig:proportioninsecure} we showed the vulnerability of devices in \da\ to known critical Android vulnerabilities.
Initially the plot is all `maybe insecure' (yellow) as since \da\ does not have historical data from before that point we cannot distinguish between devices which are running a version of Android which is known to be vulnerable but which have a backported fix and those which do not have a backported fix as we do not have data on what builds existed before the vulnerability was discovered.
This shows the importance of a longitudinal study as this analysis requires years of data.
Once \emph{zergRush} was discovered the plot goes mostly `insecure' (red) as most devices were exposed to that vulnerability but some were already running a version of Android which fixed that vulnerability and so from that point until the discovery of \emph{APK duplicate file} the graph shows progressively more `secure' green.
From that point onwards the more regular discovery of critical vulnerabilities ensures that most devices are exposed to known critical vulnerabilities.
